%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    \cventry
    {Research assistant at Institute of Physics}
    {}
    {}
    {}
    {
        I worked with Prof. Xi Dai and Prof. Lei Wang on applying machine learning method to first principle calculation, my work mainly focused on:
        \begin{itemize}
        \item Approximate kinetic energy functional for orbital free density functional theory
            \begin{itemize}
                \item Save $80\%$ training time by using automatic differentiation on Gaussian process's hyperparameters.
                \item Increase robustness of functional derivative prediction on complex situations by designing an algorithm that jointly train Gaussian process and it's derivative process.
            \end{itemize}
        \item Scientific machine learning in quantum chemistry
            \begin{itemize}
                \item Allow flexible quantum mechanics programming in \textit{Julia} and easy access to gradient information by developing \textbf{QuantumLang.jl} and integrating it with \textit{Julia}'s 'source-to-source automatic differentiation tool.
                \item Imrove the convergence rate of the Hartree Fock method by designing a density matrix based Hartree Fock algorithm.
                \item Achieve same accuracy on a $2\times$ smaller basis set by implementing a fully variational Hartree Fock method based on \textbf{QuantumLang.jl}.
                \item Obtain a $10\times$ speedup compared to a similar previous work by using \textbf{QuantumLang.jl}.
            \end{itemize}
        \end{itemize}
    }


    \cventry
    {Undergraduate student in Sichuan University}
    {}
    {}
    {}
    {
        \begin{itemize}
            \item I was supervised by Prof. Bingwei Long to study quantum few-body problem using renormalization group method
            \item I was supervised by Prof. Mingli Yang to study magnetism in transition metal cluster using first principle calculation and Monte Carlo simulation
        \end{itemize}
    }

\end{cventries}



